---
title: "`r tmp.data$rapportLabels$titre`"
author: "Pivot Science"
date: "`r tmp.data$rapportLabels$daterep`"
geometry: "margin=0.5cm"
output:
  html_document: default
  pdf_document: default
  word_document: default
sansfont: Calibri Light
---

\fontsize{9}{9}
\selectfont

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning=FALSE, message=FALSE)
```

## `r tmp.data$rapportLabels$p1`

```{r tmp.data$road.fig, out.width='100%', fig.align='center'}
if (file.exists(tmp.data$mapFile)) {
  knitr::include_graphics(tmp.data$mapFile)
}
```

```{r tmp.data$resultatParcours, results='asis'}

if (!is.null(tmp.data$resultatParcours) &&
    nrow(tmp.data$resultatParcours) > 0) {

  pander::pandoc.table(
    tmp.data$resultatParcours[, -1, drop = FALSE],
    caption = NULL,
    justify = "left",
    split.table = Inf
  )
}

```

## `r tmp.data$rapportLabels$p2`

* `r tmp.data$rapportLabels$g1` : `r tmp.data$infoRapport$Eau_de_surface`
```{r tmp.data$infoRiverLabel, results='asis'}
if (!is.null(tmp.data$infoRiverLabel) &&
    nrow(tmp.data$infoRiverLabel) > 0) {

  pander::pandoc.table(
    tmp.data$infoRiverLabel,
    caption = NULL,
    justify = "left",
    split.table = Inf
  )
}

```
* `r tmp.data$rapportLabels$g2` : **`r tmp.data$infoRapport$Foret_dense`**
* `r tmp.data$rapportLabels$g3` : **`r tmp.data$infoRapport$Savane_Arboree`**
* `r tmp.data$rapportLabels$g4` : **`r tmp.data$infoRapport$Riziere`**
* `r tmp.data$rapportLabels$g5` : **`r tmp.data$infoRapport$Zone_Habitation`**

